A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-24 tex/body.tex
tweaked

{\looseness=-1
For each goal in each theory, Sledgehammer was invoked to select up to
256~lemmas, which were monomorphized and translated to SMT-LIB~2
along with the goal \cite{blanchette-et-al-2013-smt}. The resulting problem was
given to the development version of CVC4 and to Z3 4.3.2 for comparison, each
running for up to 60 seconds on the StarExec cluster
\cite{stump-et-al-2014-starexec}.
%Problems not involving (co)datatypes were left out.
Due to the lack of machinery for reconstructing inferences about (co)datatypes
in Isabelle, the solvers are trusted as oracles. % in these experiments.
%Z3 is included for comparison.

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all three benchmark suites. It accounts for an overall
success rate increase of over \OK{5\%}, which is quite significant. For Isabelle
users, the practical usefulness of interpreted (co)datatypes is roughly
comparable to that of arithmetic \cite{blanchette-et-al-2013-smt}, although this
obviously depends a lot on the application. The raw evaluation data also
reveals that the stronger decision procedures almost completely subsume the
weaker ones in practice.

>>>>

{\looseness=-1
For each goal in each theory, Sledgehammer was invoked to select up to
256~lemmas, which were monomorphized and translated to SMT-LIB~2
along with the goal \cite{blanchette-et-al-2013-smt}. The resulting problem was
given to the development version of CVC4 and to Z3 4.3.2 for comparison, each
running for up to 60~s on the StarExec cluster
\cite{stump-et-al-2014-starexec}.
%Problems not involving any (co)datatypes were left out.
Due to the lack of machinery for reconstructing inferences about (co)datatypes
in Isabelle, the solvers are trusted as oracles. % in these experiments.
%Z3 is included for comparison.

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all three benchmark suites. It accounts for an overall
success rate increase of over \OK{5\%}, which is quite significant. For Isabelle
users, the practical usefulness of interpreted (co)datatypes is roughly
comparable to that of arithmetic \cite{blanchette-et-al-2013-smt}, although this
obviously depends on the application. The raw evaluation data also
suggest that the theoretically stronger decision procedures almost completely
subsume the weaker ones in practice.
